% +++
% sequence = ["latex", "dvipdf"]
% latex = "uplatex"
% clean_files = [
%   "%B.aux", "%B.dvi", "%B.glo", "%B.hd", "%B.idx", "%B.ind",
%   "%B.ilg", "%B.log", "%B.out", "%B.synctex.gz",
% ]
% +++
\documentclass[dvipdfmx,kernel]{wtpl3doc}
\usepackage{docmute}
%\listfiles

\begin{document}

\title{The \LaTeX3 Interfaces}
\author{%
 The \LaTeX3 Project\thanks
   {%
     E-mail:
       \href{mailto:latex-team@latex-project.org}
         {latex-team@latex-project.org}%
   }%
}
\date{Released 2020-01-22}

\pagenumbering{roman}
\maketitle

\begin{abstract}

\setlength\parindent{0pt}
\setlength\parskip{\baselineskip}

\noindent
This is the reference documentation for the \pkg{expl3}
programming environment. The \pkg{expl3} modules set up an experimental
naming scheme for \LaTeX{} commands, which allow the \LaTeX{} programmer
to systematically name functions and variables, and specify the argument
types of functions.

The \TeX{} and \eTeX{} primitives are all given a new name according to
these conventions. However, in the main direct use of the primitives is
not required or encouraged: the \pkg{expl3} modules define an
independent low-level \LaTeX3 programming language.

At present, the \pkg{expl3} modules are designed to be loaded on top of
\LaTeXe{}. In time, a \LaTeX3 format will be produced based on this code.
This allows the code to be used in \LaTeXe{} packages \emph{now} while a
stand-alone \LaTeX3 is developed.

\begin{bfseries}
  While \pkg{expl3} is still experimental, the bundle is now regarded as
  broadly stable. The syntax conventions and functions provided are now
  ready for wider use. There may still be changes to some functions, but
  these will be minor when compared to the scope of \pkg{expl3}.

  New modules will be added to the distributed version of \pkg{expl3} as
  they reach maturity.
\end{bfseries}

\end{abstract}

\clearpage

{%
  \def\\{:}% fix "newlines" in the ToC
  \tableofcontents
}

\clearpage
\pagenumbering{arabic}

\makeatletter
\def\partname{Part}
\def\maketitle{\clearpage\part{\@title}}
\let\thanks\@gobble
\let\DelayPrintIndex\PrintIndex
\let\PrintIndex\@empty
\providecommand*{\hexnum}[1]{\text{\texttt{\char`\"}#1}}
\makeatother

\input{introduction-ja.tex}

%\DocInput{l3bootstrap.dtx}
%\DocInput{l3names.dtx}
%\DocInput{l3basics.dtx}
%\DocInput{l3expan.dtx}
%\DocInput{l3tl.dtx}
%\DocInput{l3str.dtx}
%\DocInput{l3str-convert.dtx}
%\DocInput{l3quark.dtx}
%\DocInput{l3seq.dtx}
%\DocInput{l3int.dtx}
\input{l3int-ja.tex}
%\DocInput{l3flag.dtx}
%\DocInput{l3prg.dtx}
%\DocInput{l3sys.dtx}
%\DocInput{l3clist.dtx}
%\DocInput{l3token.dtx}
%\DocInput{l3prop.dtx}
%\DocInput{l3msg.dtx}
%\DocInput{l3file.dtx}
%\DocInput{l3skip.dtx}
%\DocInput{l3keys.dtx}
%\DocInput{l3intarray.dtx}
%\DocInput{l3fp.dtx}
%\DocInput{l3fparray.dtx}
%\DocInput{l3sort.dtx}
%\DocInput{l3tl-analysis.dtx}
%\DocInput{l3regex.dtx}
%\DocInput{l3box.dtx}
%\DocInput{l3coffins.dtx}
%\DocInput{l3color-base.dtx}
%\DocInput{l3luatex.dtx}
%\DocInput{l3unicode.dtx}
%\DocInput{l3text.dtx}
%\DocInput{l3legacy.dtx}
%\DocInput{l3candidates.dtx}

% 終了部
\clearpage

\begingroup
  \def\endash{--}
  \catcode`\-\active
  \def-{\futurelet\temp\indexdash}
  \def\indexdash{\ifx\temp-\endash\fi}
  \DelayPrintIndex
\endgroup

\end{document}
